---
title: "tmap-intro"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tmap-intro}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The function currently only works with the interactive mode in tmap, as that is is its primary use case. A static mode may be worth developing but as we mostly use tmap for interactive purposes and ESRI for static it may be wasted effort. 

The package will create a base map without loading tmap but to use the base map you should load tmap and set it to interactive.

```{r setup}
library(rpgmapr)
library(tmap);tmap_mode("view")
library(tidycensus)
library(tidyverse)
library(osmdata)

# pull sample data for mapping

miami <- get_acs(
  state = "FL",
  county = "Miami-Dade",
  geography = "tract",
  variables = "B19013_001",
  geometry = TRUE,
  year = 2020
) %>% 
  filter(!is.na(estimate))

cycleways <- opq('Miami-Dade') %>%
  add_osm_feature(key = 'highway', value = 'cycleway') %>% 
  osmdata_sf() %>% 
  .$osm_lines %>% 
  select(osm_id, geometry) 

#create random ridership numbers

ridership <- rnorm(nrow(cycleways), mean = 1000, sd = 200)

cycleways <- cycleways %>% 
  mutate(ridership = sample(ridership))
```

### Basic Usage

The main use is to create a simple base map object that can be passed to further processing. This is as easy as the code below

```{r}
base <- create_tmap_base()
```

This creates a flat base map layer that can used similarly to the below code.

```{r}
base + 
  tm_shape(miami) + 
  tm_polygons(col = "estimate",
              palette = "plasma",
              alpha = 0.5,
              n = 10,
              lwd = 0.5)
```

However these flat base map keep all elements below the displayed data, more complex base map objects can be created with minimal effort.

```{r}
base <- create_tmap_base(
  type = "base_detailed"
)

base + 
  tm_shape(miami) + 
  tm_polygons(col = "estimate",
              palette = "plasma",
              alpha = 0.5,
              n = 10,
              lwd = 0.5)
```

For maps of roadways and other line features roads can be turned off to increase readability.

```{r}
base <- create_tmap_base(
  type = "base_detailed",
  lines = FALSE
)

base + 
  tm_shape(cycleways) + 
  tm_lines(col = "ridership",
           palette = "plasma",
           n = 10,
           lwd = 2)
```

Multiple layers can be used as well. For these complicated maps it may be worth using a simpler base map, see `TODO insert url` for all available styles.

```{r}
base <- create_tmap_base(
  type = "base_simple",
  lines = FALSE
)

base + 
  tm_shape(miami) + 
  tm_polygons(col = "estimate",
              palette = "plasma",
              alpha = 0.5,
              n = 10,
              lwd = 0.5) +
  tm_shape(cycleways) + 
  tm_lines(lwd = "ridership",
           palette = "plasma",
           scale = 3)
```










